PANCHANGE_data_preprocessing

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
renamed all sums cores to sum_score_raw

# Calulate total score
pcl.scored_items_prepan <- scoreItems(keys = pcl.items_key_prepan,
                                        items = glad.pcl.raw.id[pcl.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 1, 
                                        max = 5)
# Add in column to tibble
glad.pcl.raw.id$pcl.sum_score_prepan <- pcl.scored_items_prepan$scores

# Look at values
glad.pcl.raw.id %>%
  descr(pcl.sum_score_prepan,
        stats = "common"
        )
```

@@

@@

# Calulate sum score
phq.scored_items_prepan <- scoreItems(keys = phq.items_key_prepan,
                                        items = glad.phq.raw.id[phq.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
glad.phq.raw.id$phq.sum_score_prepan <- phq.scored_items_prepan$scores

# Look at values
glad.phq.raw.id %>%
  descr(phq.sum_score_prepan,
        stats = "common"
        )
```

@@

# Calulate total score
gad.scored_items_retro <- scoreItems(keys = gad.items_key_retro,
                                        items = coping.glad.gad.raw.id[gad.items_retro],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
coping.glad.gad.raw.id$gad.sum_score_retro <- gad.scored_items_retro$scores

# Look at values
coping.glad.gad.raw.id %>%
  descr(gad.sum_score_retro,
        stats = "common"
        )
```

@@

# Calulate total score
gad.scored_items_base <- scoreItems(keys = gad.items_key_base,
                                        items = coping.glad.gad.raw.id[gad.items_base],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
coping.glad.gad.raw.id$gad.sum_score_base <- gad.scored_items_base$scores

# Look at values
coping.glad.gad.raw.id %>%
  descr(gad.sum_score_base,
        stats = "common"
        )
```

@@

# Calulate total score
pcl.scored_items_retro <- scoreItems(keys = pcl.items_key_retro,
                                     items = coping.glad.pcl.raw.id[pcl.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 1)
# Add in column to tibble
coping.glad.pcl.raw.id$pcl.sum_score_retro <- pcl.scored_items_retro$scores

# Look at values
coping.glad.pcl.raw.id %>%
  descr(pcl.sum_score_retro,
        stats = "common"
  )
```

@@

# Calulate total score
pcl.scored_items_base <- scoreItems(keys = pcl.items_key_base,
                                    items = coping.glad.pcl.raw.id[pcl.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = "none", 
                                    min = 1, 
                                    max = 5)
# Add in column to tibble
coping.glad.pcl.raw.id$pcl.sum_score_base <- pcl.scored_items_base$scores

# Look at values
coping.glad.pcl.raw.id %>%
  descr(pcl.sum_score_base,
        stats = "common"
  )
```

@@

# Calulate total score
phq.scored_items_retro <- scoreItems(keys = phq.items_key_retro,
                                     items = coping.glad.phq.raw.id[phq.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 3)
# Add in column to tibble
coping.glad.phq.raw.id$phq.sum_score_retro <- phq.scored_items_retro$scores

# Look at values
coping.glad.phq.raw.id %>%
  descr(phq.sum_score_retro,
        stats = "common"
  )
```

@@

# Calulate total score
phq.scored_items_base <- scoreItems(keys = phq.items_key_base,
                                    items = coping.glad.phq.raw.id[phq.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 0, 
                                    max = 3)
# Add in column to tibble
coping.glad.phq.raw.id$phq.sum_score_base <- phq.scored_items_base$scores

# Look at values
coping.glad.phq.raw.id %>%
  descr(phq.sum_score_base,
        stats = "common"
  )
```

@@

# Calulate total score
ocir.scored_items_retro <- scoreItems(keys = ocir.items_key_retro,
                                     items = coping.glad.ocir.raw.id[ocir.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 4)
# Add in column to tibble
coping.glad.ocir.raw.id$ocir.sum_score_retro <- ocir.scored_items_retro$scores

# Look at values
coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_retro,
        stats = "common"
  )
```

@@

# Calulate total score
ocir.scored_items_base <- scoreItems(keys = ocir.items_key_base,
                                    items = coping.glad.ocir.raw.id[ocir.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 0, 
                                    max = 4)
# Add in column to tibble
coping.glad.ocir.raw.id$ocir.sum_score_base <- ocir.scored_items_base$scores

# Look at values
coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_base,
        stats = "common"
  )
```

>>>>

# Calulate total score
pcl.scored_items_prepan <- scoreItems(keys = pcl.items_key_prepan,
                                        items = glad.pcl.raw.id[pcl.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 1, 
                                        max = 5)
# Add in column to tibble
glad.pcl.raw.id$pcl.sum_score_prepan_raw <- pcl.scored_items_prepan$scores

# Look at values
glad.pcl.raw.id %>%
  descr(pcl.sum_score_prepan_raw,
        stats = "common"
        )
```

@@

```{r pcl prepan sum score if missigng items set to NA}
glad.pcl.raw.id <- glad.pcl.raw.id %>%
  mutate(
    pcl.sum_score_prepan =
      if_else(condition = na_per_person_pcl_prepan > 0,
              true = NA_real_,
              false = pcl.sum_score_prepan_raw,
              missing = NA_real_
      )
  )

glad.pcl.raw.id %>%
  descr(pcl.sum_score_prepan_raw, stats = "common")

glad.pcl.raw.id %>%
  descr(pcl.sum_score_prepan, stats = "common")
```

@@

# Calulate sum score
phq.scored_items_prepan <- scoreItems(keys = phq.items_key_prepan,
                                        items = glad.phq.raw.id[phq.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
glad.phq.raw.id$phq.sum_score_prepan_raw <- phq.scored_items_prepan$scores

# Look at values
glad.phq.raw.id %>%
  descr(phq.sum_score_prepan_raw,
        stats = "common"
        )
```

@@

# Calulate total score
gad.scored_items_retro <- scoreItems(keys = gad.items_key_retro,
                                        items = coping.glad.gad.raw.id[gad.items_retro],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
coping.glad.gad.raw.id$gad.sum_score_retro_raw <- gad.scored_items_retro$scores

# Look at values
coping.glad.gad.raw.id %>%
  descr(gad.sum_score_retro_raw,
        stats = "common"
        )
```

@@

# Calulate total score
gad.scored_items_base <- scoreItems(keys = gad.items_key_base,
                                        items = coping.glad.gad.raw.id[gad.items_base],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
coping.glad.gad.raw.id$gad.sum_score_base_raw <- gad.scored_items_base$scores

# Look at values
coping.glad.gad.raw.id %>%
  descr(gad.sum_score_base_raw,
        stats = "common"
        )
```

@@

# Calulate total score
pcl.scored_items_retro <- scoreItems(keys = pcl.items_key_retro,
                                     items = coping.glad.pcl.raw.id[pcl.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 1)
# Add in column to tibble
coping.glad.pcl.raw.id$pcl.sum_score_retro_raw <- pcl.scored_items_retro$scores

# Look at values
coping.glad.pcl.raw.id %>%
  descr(pcl.sum_score_retro_raw,
        stats = "common"
  )
```

@@

# Calulate total score
pcl.scored_items_base <- scoreItems(keys = pcl.items_key_base,
                                    items = coping.glad.pcl.raw.id[pcl.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = "none", 
                                    min = 1, 
                                    max = 5)
# Add in column to tibble
coping.glad.pcl.raw.id$pcl.sum_score_base_raw <- pcl.scored_items_base$scores

# Look at values
coping.glad.pcl.raw.id %>%
  descr(pcl.sum_score_base_raw,
        stats = "common"
  )
```

@@

# Calulate total score
phq.scored_items_retro <- scoreItems(keys = phq.items_key_retro,
                                     items = coping.glad.phq.raw.id[phq.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 3)
# Add in column to tibble
coping.glad.phq.raw.id$phq.sum_score_retro_raw <- phq.scored_items_retro$scores

# Look at values
coping.glad.phq.raw.id %>%
  descr(phq.sum_score_retro_raw,
        stats = "common"
  )
```

@@

# Calulate total score
phq.scored_items_base <- scoreItems(keys = phq.items_key_base,
                                    items = coping.glad.phq.raw.id[phq.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 0, 
                                    max = 3)
# Add in column to tibble
coping.glad.phq.raw.id$phq.sum_score_base_raw <- phq.scored_items_base$scores

# Look at values
coping.glad.phq.raw.id %>%
  descr(phq.sum_score_base_raw,
        stats = "common"
  )
```

@@

# Calulate total score
ocir.scored_items_retro <- scoreItems(keys = ocir.items_key_retro,
                                     items = coping.glad.ocir.raw.id[ocir.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 4)
# Add in column to tibble
coping.glad.ocir.raw.id$ocir.sum_score_retro_raw <- ocir.scored_items_retro$scores

# Look at values
coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_retro_raw,
        stats = "common"
  )
```

@@

# Calulate total score
ocir.scored_items_base <- scoreItems(keys = ocir.items_key_base,
                                    items = coping.glad.ocir.raw.id[ocir.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 0, 
                                    max = 4)
# Add in column to tibble
coping.glad.ocir.raw.id$ocir.sum_score_base_raw <- ocir.scored_items_base$scores

# Look at values
coping.glad.ocir.raw.id %>%
  descr(ocir.sum_score_base_raw,
        stats = "common"
  )
```
